\markdownRendererDocumentBegin
\markdownRendererJekyllDataBegin\markdownRendererJekyllDataMappingBegin{null}{2}\markdownRendererJekyllDataString{_date}{20-28}\markdownRendererJekyllDataString{_title}{test}\markdownRendererJekyllDataMappingEnd\markdownRendererJekyllDataEnd\markdownRendererInterblockSeparator
{}\markdownRendererHeadingOne{University Scripting Workflow}\markdownRendererInterblockSeparator
{}I am going to create a semi-automated lecture and file organiser. \markdownRendererBackslash{} \markdownRendererBackslash{} This will be used to generate my file structure for each module, and generate a \markdownRendererStrongEmphasis{master.tex} file that will include the two most recent lecture notes. \markdownRendererBackslash{} \markdownRendererBackslash{} Additionally, there will be an option to generate a complete pdf of all my lecture notes for one module. \markdownRendererBackslash{} \markdownRendererBackslash{} Finally, it will symlink the current or most recent module to the current course directory. \markdownRendererBackslash{} \markdownRendererBackslash{} Python and possibly shell script will be used for this process. \markdownRendererBackslash{} \markdownRendererBackslash{} I may need to use cron to schedule events.\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Processes:}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Add lectures, any directories, compiled lectures, master.tex and preamble.tex to each module directory.\markdownRendererUlItemEnd 
\markdownRendererUlItem Change output directory of compiled tex docs.\markdownRendererUlItemEnd 
\markdownRendererUlItem Update each master.tex with the two most recent lecture notes.\markdownRendererUlItemEnd 
\markdownRendererUlItem Option to compile master.tex with all the lecture notes.\markdownRendererUlItemEnd 
\markdownRendererUlItem Update current module with the current module for ease of access - look into calendar API or use the day.\markdownRendererUlItemEnd 
\markdownRendererUlItem Change working path based on date.\markdownRendererUlItemEnd 
\markdownRendererUlItem Automatically symlink year long courses from semesters into year long directory.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{TODO}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Add latex files to directories\markdownRendererUlItemEnd 
\markdownRendererUlItem Exclude master.tex from year long directory\markdownRendererUlItemEnd 
\markdownRendererUlItem Add preambles\markdownRendererUlItemEnd 
\markdownRendererUlItem Add master.tex to lectures\markdownRendererUlItemEnd 
\markdownRendererUlItem Automatically change master.tex files\markdownRendererUlItemEnd 
\markdownRendererUlItem Option to compile big master.tex\markdownRendererUlItemEnd 
\markdownRendererUlItem Change tex output directory\markdownRendererUlItemEnd 
\markdownRendererUlItem Path.suffix may be useful for dealing with tex files\markdownRendererUlItemEnd 
\markdownRendererUlItem incorporate tex functions incase i choose to use tex still\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Alterations to the original spec}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem I may take notes in markdown instead of latex\markdownRendererUlItemEnd 
\markdownRendererUlItem Use github pages to host these markdown pages, in combination with jekyll\markdownRendererUlItemEnd 
\markdownRendererUlItem Maybe do current module inside of lectures class\markdownRendererUlItemEnd 
\markdownRendererUlItem And year long inside lectures class? Or as a module class function\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingOne{Adding markdown notes to LaTeX doc ->}\markdownRendererInterblockSeparator
{}\markdownRendererBackslash{}usepackage\markdownRendererLeftBrace{}markdown\markdownRendererRightBrace{} \markdownRendererBackslash{}begin\markdownRendererLeftBrace{}document\markdownRendererRightBrace{} \markdownRendererBackslash{}markdownInput\markdownRendererLeftBrace{}lec1.md\markdownRendererRightBrace{} \markdownRendererBackslash{}end\markdownRendererLeftBrace{}document\markdownRendererRightBrace{}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Then run this command: latexmk -cd -lualatex -silent path/master.tex\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererDocumentEnd